Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS

### 2022-04-14 outputs/paper/Kenya_DHS_1998.Rmd
“update“

---
title: "Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS"
subtitle: "An Analysis Based on the Kenya's Demographic and Health Survey in 1998"
author: 
  - Charles Lu
  - Mahak Jain
  - Yujun Jiao
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Using data extracted from Kenya’s Demographic and Health Surveys in 1998, this analysis aims to study the Kenyans’ perception of their risk of getting AIDS. By analyzing the age, marital status, number of sex partners, residence, province, and education of the survey’s participants, results show that these factors all have different levels of impact on people’s risk of being infected. R [@citeR] is used in this report to create visualizations for the results. In the future, this report can help scholars to dive deeper into the history of the sexually-transmissible disease, study the correlation between the transmission rate and social backgrounds, and aid the authorities in making governmental or health-related plans. "
header-includes:
  - \usepackage{placeins}
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: true
    fig_caption: yes
bibliography: references.bib
thanks: "https://github.com/R300G/Kenya_Demographic_1998"
---

@@

While advocating changes to future health-related plans, it's also important to look back into the past to study the people's reactions, perceptions, and responses to similar matters in the past century. In the Kenya Demographic and Health Survey conducted in 1998, survey answers were collected to reflect the demographic, health, and living conditions of the average Kenyans[@DHS]. More precisely, this report extracts data from chapter 10 of the survey report, where Aids and other sexually transmitted diseases were discussed in detail. By using a data set taken and cleaned from two tables titled "AIDS-related knowledge," this report aims to analyze the impacts of genders, age groups, marital status, number of sexual partners, residence regions, provinces and education levels on people's perception of the risk of getting AIDs. In other words, this report analyzes the question: what are the chances of getting AIDS for people from different backgrounds? This report utilizes analytic programming language R [@citeR]. R packages tidyverse [@tidyverse], janitor [@janitor] and dplyr [@dplyr] are used to clean, organize and manipulate the data. Furthermore, R packages ggplot2 [@ggplot2], scales [@scales] and knitr [@knitr] are used to create figures and tables. R packages bookdown [@bookdown] and tinytex [@tinytex] are used to generate the R markdown Report.

By studying the many ways in which the knowledge of Aids can be influenced by the participants’ personal backgrounds, this report came to the conclusion that all the variables presented in the report have an impact on people’s perception of their chances of getting AIDS. As controlling the spread of AIDS is one of the most compelling topics in modern society, it’s exceedingly important to deconstruct the risk of catching the virus for people with different lifestyles and backgrounds.

@@

## What is done in this paper?

@@

## What is something we learn about the world?

@@

AIDS is a transmissible disease that cannot be cured. Being a dreadful disease that has infected more than 35 million people worldwide, it can only be controlled with active therapy and medications[@deeks]. In this report, by analyzing the answers from people from various backgrounds, the chances of them being infected with AIDS were analyzed in detail. However, studying people’s perceptions alone is not enough to make fair conclusions about the nature, the trends, and the effective prevention methods of the disease. Other factors such as people’s knowledge about AIDS, the universalization rate of effective prevention methods, and the availability of healthcare in the studied region are also crucial to the impacts of the disease. In addition, the DHS report studied in this analysis was published in 1998, signifying that it has lost some relevance to modern society. Hence, in the future, more up-to-date reports will be reviewed to achieve a better understanding of the different aspects of the disease. In hopes of reducing the negative influence of AIDS on people’s daily life, this analysis aims to educate the public about the seriousness of sexually transmissible diseases, outline the factors that increase the infection rate, and promote future governmental and health plans.

>>>>

---
title: "Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS"
subtitle: "An Analysis Based on the Kenya's Demographic and Health Survey in 1998"
author: 
  - Charles Lu
  - Mahak Jain
  - Yujun Jiao
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Using data extracted from Kenya’s Demographic and Health Surveys in 1998, this analysis aims to study the Kenyans’ perception of their risk of getting AIDS. By analyzing the age, marital status, number of sex partners, residence, province, and education of the survey’s participants, results show that these factors all have different levels of impact on people’s risk of being infected. R [@citeR] is used in this report to create visualizations for the results. In the future, this report can help scholars to dive deeper into the history of the sexually-transmissible disease, study the correlation between the transmission rate and social backgrounds, and aid the authorities in making governmental or health-related plans. "
header-includes:
  - \usepackage{placeins}
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: true
    fig_caption: yes
bibliography: references.bib
thanks: " The data and code that support this report can be found in the Github repository: https://github.com/R300G/Kenya_Demographic_1998"
---

@@

While advocating changes to future health-related plans, it's also important to look back into the past to study the people's reactions, perceptions, and responses to similar matters in the past century. In the Kenya Demographic and Health Survey conducted in 1998, survey answers were collected to reflect the demographic, health, and living conditions of the average Kenyans[@DHS]. More precisely, this report extracts data from chapter 10 of the survey report, where AIDs and other sexually transmitted diseases were discussed in detail. By using a data set taken and cleaned from two tables titled "AIDS-related knowledge," this report aims to analyze the impacts of genders, age groups, marital status, number of sexual partners, residence regions, provinces and education levels on people's perception of the risk of getting AIDS. In other words, this report analyzes the question: what are the chances of getting AIDS for people from different backgrounds? This report utilizes analytic programming language R [@citeR]. R packages tidyverse [@tidyverse], janitor [@janitor] and dplyr [@dplyr] are used to clean, organize and manipulate the data. Furthermore, R packages ggplot2 [@ggplot2], scales [@scales] and knitr [@knitr] are used to create figures and tables. R packages bookdown [@bookdown] and tinytex [@tinytex] are used to generate the R markdown Report.

By studying the many ways in which the knowledge of AIDS can be influenced by the participants’ personal backgrounds, this report came to the conclusion that all the variables presented in the report have an impact on people’s perception of their chances of getting AIDS. As controlling the spread of AIDS is one of the most compelling topics in modern society, it’s exceedingly important to deconstruct the risk of catching the virus for people with different lifestyles and backgrounds.

@@

## Summary

@@

## HIV/AIDS in Kenya

@@

AIDS is a transmissible disease that cannot be cured. AIDS/HIV has infected more than 35 million people worldwide, it can only be controlled with active therapy and medications[@deeks]. In this report, by analyzing the answers from people from various backgrounds, the chances of them being infected with AIDS were analyzed in detail. However, studying people’s perceptions alone is not enough to make fair conclusions about the nature, the trends, and the effective prevention methods of the disease. Other factors such as people’s knowledge about AIDS, the universalization rate of effective prevention methods, and the availability of healthcare in the studied region are also crucial to the impacts of the disease. In addition, the DHS report studied in this analysis was published in 1998, signifying that it has lost some relevance to modern society. Hence, in the future, more up-to-date reports will be reviewed to achieve a better understanding of the different aspects of the disease. In hopes of reducing the negative influence of AIDS on people’s daily life, this analysis aims to educate the public about the seriousness of sexually transmissible diseases, outline the factors that increase the infection rate, and promote future governmental and health plans.
